%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Self Project}  
    {Omeclone} % 
    {GECA, India} % Location
    {Sept’ 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Real time messaging web application for active users.}
        \item {Implemented using Node.js + Express.}
        \item {{\em Technologies used}: Socket.io, that enables real-time, bidirectional communication. }
        \item {{\em Deployed at}:\href{https://omecloneio.herokuapp.com/}{ omecloneio.herokuapp.com}}
        \item {{\em Link}:\href{https://github.com/purveshmakode24/omeclone}{ github.com/purveshmakode24/omeclone}} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Task} % Job title
    {I.S.R.A.P.L (Website)} % Organization
    {GECA, India} % Location
    {Aug’ 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A website which I’ve developed for my class teacher when I was in 3rd semester. }
        \item {It’s a simple website gives you brief information about {\em Indian Social Reformers and Political Leaders}.}
        \item {Implemented using HTML, CSS, JavaScript and some modern CSS Framework.}
        \item {Link:\href{https://github.com/PurveshMakode24/israpl-site}{ github.com/PurveshMakode24/israpl-site}}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry     
    {Self Project} % Job title
    {Node-Darksky} % Organization
    {GECA, India} % Location
    {Aug’ 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Help getting an idea of weather for your area/city. Just enter your city name and you are done.}
        \item {It's a simple Node.js + Express real time web application.}
        \item {Used Open-weather Map's API, that enables us to Access current weather data for any location including over 200,000 cities.}
        \item {{\em Deployed at}:\href{https://node-darksky.herokuapp.com/}{ node-darksky.herokuapp.com}}
        \item {{\em Link}:\href{https://github.com/purveshmakode24/node-darksky}{ github.com/purveshmakode24/node-darksky}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
 	{Self Project}  
    {Chatbot Application} % 
    {GECA, India} % Location
    {Feb’ 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {A simple messenger (chat-bot) server-side web application used to connect with friends.}
        \item {Implemented using html, CSS, MariaDB, XAMPP server and a server written in PHP.}
        \item {Link:\href{https://github.com/PurveshMakode24/chatbot-application}{ github.com/PurveshMakode24/chatbot-application}} 
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
